Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-03-14 doc/manuscript/ESSDmanuscript.Rmd
manuscript
finally got it to knit!

# Mapping ForC to EFDB

>>>>

# Mapping ForC to EFDB
ForC data is incredibly valuable to EFDB and there is data which is included in the ForC database that does not meet EFDB standards. There were two main EFDB guidelines which limits the amount of data we could transfer. EFDB will not accept data which has been digitized(from graph) and ForC does.

### 2022-03-14 doc/manuscript/ESSDmanuscript.tex
trying 2 knit
manuscript
finally got it to knit!

Soil organic matter is defined as\ldots{}

@@

>>>>

Soil organic matter is defined as ``Includes organic carbon in mineral
and organic soils (including peat) to a specified depth chosen by the
country and applied consistently through the time series. Live fine
roots (of less than the suggested diameter limit for belowground
biomass) are included with soil organic matter where they cannot be
distinguished from it empirically.''(2003 IPCc GPG for LULUCF
(https://www.ipcc-nggip.iges.or.jp/public/gpglulucf/gpglulucf\_files/Glossary\_Acronyms\_BasicInfo/Glossary.pdf)

@@

ForC data is incredibly valuable to EFDB and there is data which is
included in the ForC database that does not meet EFDB standards. There
were two main EFDB guidelines which limits the amount of data we could
transfer. EFDB will not accept data which has been digitized(from graph)
and ForC does.
